Disentangling the spinal mechanisms of illusory heat and burning sensations in the Thermal Grill Illusion

### 2024-01-10 Manuscript.Rmd
adding thresholds as supplementary figure
suggested changesø

# Figure2
sPlot(include_zero = T)
```

@@

plot1(include_zero = F)
#plot1(include_zero = T)

@@

plot2_3(include_zero = F)[[1]]
```

@@

plot2_3(include_zero = F)[[2]]
```

@@

>>>>

# Figure2
f2_plot(include_zero = T)
```

@@

f3_plot(include_zero = F)
#plot1(include_zero = T)

@@

f45_plot(include_zero = F)[[1]]
```

@@

f45_plot(include_zero = F)[[2]]
```

@@

\newpage
## Temperatures by participant

```{r, results="hide", fig.width = 7.2, fig.height = 5, warning = F, message = F, echo = F, fig.cap = "Figure S1: Pain thresholds (left) and TGI temperatures (right) for each participant in experiment 1 and experiment 2. As we did not go below 5ºC or above 45ºC for the TGI stimuli, CPT and HPT were capped at 5ºC and 45ºC respectively"}

sPlot1(include_zero = F)
```
